---
title: "Importing data from Excel using XLConnect"
author: "Huruy Belay"
date: "June 28, 2017"
output: html_document
---
```{r, message=FALSE}
library(XLConnect)
```

We can import excel data to R and analyzed the whole data in R using read_excel. However, if we force to do our analysis in excel but you want to do your analysis in R, I am happy to share you that there is a way to connect the excel data to R using XLConnect.

The following are the steps to connect the: excel to R:

#### Step-1: To connect to the excel 

```{r}
data<-loadWorkbook("summary.xlsx")
```

* We can read the sheets of the excel

```{r}
getSheets(data)
```

#### Step-2: Reading the data from the sheet we want

To read from each table we will use the following R programs. We can call the sheet number or the sheet name.

```{r}
sheet1 <- readWorksheet(data, sheet = 1) # or sheet1 <- readWorksheet(data, sheet = "1960-1966") 
sheet2 <- readWorksheet(data, sheet = 2)
sheet3 <- readWorksheet(data, sheet = 3)
sheet4 <- readWorksheet(data, sheet = 4)
```

After reading our data, we can manipulate the following:

#### Step-3: creating new variable

```{r}
createSheet(data, "new")
```

#### Step-4: Creating data in the new created sheet

```{r}
Ind <- data.frame(pop1= c(100000,21000000, 3000000))
writeWorksheet(data, Ind, sheet = "new")
saveWorkbook(data, file = "new_data.xlsx")
```

#### Step-5: Renaming sheet

```{r}
renameSheet(data, "1960-1966", "sheet_1")
saveWorkbook(data, file = "new.xlsx")
```

#### Step-6: Removing sheet

```{r}
removeSheet(data, sheet = "newsheet_1")
saveWorkbook(data, file = "new1.xlsx")
